

\documentclass{beamer}


\usetheme{default}

\title{Soft Computing}


\subtitle{Genetic Algorithm}

\author{By Kalpana Paliwal}


\date{\today}

\subject{Theoretical Computer Science}

\AtBeginSubsection[]
{
  \begin{frame}<beamer>{Outline}
    \tableofcontents[currentsection,currentsubsection]
  \end{frame}
}


\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Outline}
  \tableofcontents
 
\end{frame}

\section{Introduction}

\subsection{Biological relation with GA}

\begin{frame}{Introduction}{Biological relation}
  \begin{itemize}
  \item {
   Population:-set of input data
  }
  \item {
  Chromosome:- Individual input
  }
  \end{itemize}
\end{frame}

\subsection{Operators}


\begin{frame}{Operators}
  \begin{itemize}
  \item {
   Selection Operator
    \pause 
  }
  \item {   
   Mutation Operator
  }
 
  \item<3-> {
   Crossover Operator
  }
  \item<4-> {
  Reproduction Operator
  }
 
  
  \end{itemize}
\end{frame}

\section{Genetic Algorithm}

\subsection{Theorem}

\begin{frame}{Genetic Algorithm}
\begin{block}{What is GA?}
Adaptive heuristic search algorithm based on the evolutionary ideas of natural selection and genetics

\end{block}
\end{frame}
\begin{frame}
\begin{theorem}
\begin{itemize}
\item{
[Start] Generate random population of n chromosomes. 
}
\item{
[Fitness] Evaluate the fitness f(x) of each chromosome x in the population. 
}
\item{
[New population] Create 	a new population by repeating following  steps until the new population is complete. 
\begin{itemize}
\item [Selection] Select chromosomes from a population according to their fitness (better the fitness, bigger the chance to be selected) .
\item [Crossover] With a crossover probability, crossover the parents to form new offspring (children). 
\item [Mutation] With a mutation probability, mutate new offspring at each locus (position in chromosome/genes). 
\item [Accepting] Place new offspring in the new population.

\end{itemize}
}

\item{
[Replace] Use new generated population for a further run of the algorithm.
}
\item{
[Test] If the end condition is satisfied, stop, and return the best solution in current population.
}
\item{
[Loop] Go to step 2. 
}
\end{itemize}

\end{theorem}
\end{frame}


\section*{Application}

\begin{frame}{Application}
  \begin{itemize}
  \item
  Traveling Salesman Problem (TSP), 
  \item
Circuit design,
  \item
Job shop scheduling,
  \item
Minimum spanning tree,
  \item
Time table designing,
  \item
Video and sound quality optimization. 

 
  \end{itemize}
  
 
 
\end{frame}

\begin{frame}
Thank you
\end{frame}





\end{document}


